Hydras \& Co.

### 2022-02-27 doc/gaia-chapter.tex
corrections in gaia-chapter

The modules are located in {\texttt{theories/gaia/*.v}}.
The main entry point is
\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge}, which requires both Gaia's \texttt{ssete9} and a few modules of \texttt{theories/ordinals/Epsilon0}.

Other modules are dedicated to the adaptation of several notions of \HydrasLib to \mathcomp's and \gaia's vocabulary and structures.
By default, we give priority to \gaia's notation and vocabulary.

@@

@@

The following cancel lemmas will be often used in order to simplify sub-terms of the form (\texttt{g2h (h2g {\it t})}) and (\texttt{h2g (g2h {\it t})}) which appear in many proofs by rewriting.

@@

The function \texttt{g2h} is also used to provide a ``pretty'' printing of Cantor normal forms (through \texttt{Epsilon0.T1.pp}).

@@

@@

\section{Importing Material from \Hydras}

In the following two examples, the bare name \texttt{T1} is given by default either  to \HydrasLib' world or \gaia's.

\begin{itemize}
\item In
  \href{../theories/html/gaia_hydras.GaiaToHydra.html}%
  {\texttt{gaia\_hydras.GaiaToHydra}}, we adopt \HydrasLib's point of view, and the name \texttt{T1} is by default bound to
\HydrasLib' data structures.

\inputsnippets{GaiaToHydra/T1BridgeUse,
  GaiaToHydra/LocateT1}

Section~\ref{sect:gaia2hydra} shows how lemmas on arithmetic properties of ordinals strictly less than $\epsilon_0$ are  imported from \gaia , with \HydrasLib's notations.

\item The other way, the module \href{../theories/html/gaia_hydras.GCanon.html}%
  {\texttt{gaia\_hydras.GCanon}} is an adaptation to \gaia of
  \href{../theories/html/hydras.Epsilon0/Canon.html}%
  {\texttt{hydras.Epsilon0/Canon}}.
  In this module, the name \texttt{T1} is bound by default to \gaia's meaning. \HydrasLib' name \texttt{T1} is renamed into \texttt{hT1}.

  The following lemmas are expressed in \gaia's vocabulary.
  \inputsnippets{GCanon/gcanonLimitMono,
    GCanon/gcanonLimitOf}

\end{itemize}

\subsection{Data refinement}

Please note that in this module, we favour \gaia's notations over hydra's. A snippet like \texttt{(alpha < succ beta)} should be interpreted as \texttt{(T1lt alpha beta)}, where \texttt{T1lt} is defined in ~\href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{\texttt{gaia.ssete9.v}}.

@@

\subsection{Looking for a lemma}
\coq's command \texttt{Search} and notation scopes allow you to explore both libraries.

>>>>

The modules are located in {\texttt{theories/gaia/*.v}}.
The main entry point is
\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge}, which requires both Gaia's \texttt{ssete9} and a few modules of \texttt{theories/ordinals/Epsilon0}.
Other modules are dedicated to the adaptation of several notions of \HydrasLib to \mathcomp's and \gaia's vocabulary and structures.
By default, we give priority to \gaia's notation and vocabulary.

@@

Please keep in mind that, in this module, we favour \gaia's notations over hydra's. A snippet like \texttt{(alpha < succ beta)} should be interpreted as \texttt{(T1lt alpha beta)}, where \texttt{T1lt} is defined in ~\href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{\texttt{gaia.ssete9.v}}.

@@

The following cancel lemmas will be often applied in order to simplify sub-terms of the form (\texttt{g2h (h2g {\it t})}) and (\texttt{h2g (g2h {\it t})}), which appear in many proofs by rewriting.

@@

\subsubsection{Pretty printing Cantor normal forms}

The function \texttt{g2h} is also used to provide a ``pretty'' printing of Cantor normal forms (please see Sect.~\vref{sect:ppT1}).

@@

\subsubsection{Kind of refinement}

@@

@@

\subsection{Looking for a lemma}
\coq's command \texttt{Search} and notation scopes allow you to explore both libraries.
For instance, let us look for lemmas whose conclusion is
$\alpha \times \beta=\beta$.
